Reproducible Plant Pathology

### 2017-07-05 README.rmd
Cleanup README.Rmd
Remove a few badges and fix commented out text regarding Docker

[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/phytopathology/Reproducible.Plant.Pathology/commits/master) 
[![minimal R version](https://img.shields.io/badge/R%3E%3D-`r as.character(getRversion())`-brightgreen.svg)](https://cran.r-project.org/)
[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/) 
[![Travis-CI Build Status](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology.svg?branch=master)](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology)

## Research compendium for a report on the reproducibility of research in plant pathology

@@

The package has a number of dependencies on other R packages, and programs
outside of R. These are listed at the bottom of this README. Installing these can be time-consuming and complicated, so we've done two things to simplify access to the compendium. First is the `packrat/` directory, which contains the
source code for all the packages we depend on. If all works well, these will be
installed on your computer when you open `Reproducible.Plant.Pathology.Rproj` in RStudio. <!--- Second is our Docker image that includes all the necessary software, code and data to run our analysis. The Docker image may give a quicker entry point to the project, and is more self-contained, so might save some fiddling with installing things.

>>>>

[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/) 
[![Travis-CI Build Status](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology.svg?branch=master)](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology)

## A research compendium for a report on the reproducibility of research in plant pathology

@@

The package has a number of dependencies on other R packages, and programs
outside of R. These are listed at the bottom of this README. Installing these can be time-consuming and complicated, so we've done two things to simplify access to the compendium. First is the `packrat/` directory, which contains the
source code for all the packages we depend on. If all works well, these will be
installed on your computer when you open `Reproducible.Plant.Pathology.Rproj` in RStudio.

<!--- Second is our Docker image that includes all the necessary software, code and data to run our analysis. The Docker image may give a quicker entry point to the project, and is more self-contained, so might save some fiddling with installing things.
